Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-13 robdml.tex
pp7
tex

\begin{figure}[t]
	\vspace{-1.5em}
	\includegraphics[width=\columnwidth]{figgaeff.pdf}
	\vspace{-1.9em}
	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]'' in
	\cref{tab:gaeff}.}
	\label{fig:gaeff}
\end{figure}

\noindent\textbf{II. Gradual Adversary.}
%
HM[$\mathcal{S},\mathcal{M}$] may still
suffer from the imbalance between learning the embeddings and gaining
adversarial robustness as discussed in \cref{sec:32}.
%
Hence, we conduct further experiments %with an improved $H_\mathsf{D}$
following the discussion, as shown in \cref{tab:gaeff} and \cref{fig:gaeff}.
%
Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness
with $g_\mathsf{B}(\cdot)$ benefits the ERS, but
results in a notably lower R@1;
%
A constant $H_\mathsf{D}$ at the upper bound of Semihard (\ie, $0$; too high
for both the early and the late phase of training) renders model collapse;
%
$H_\mathsf{D}$ at the lower bound (\ie, $-\gamma$; too low for the late phase)
leads to insignificant ERS improvement;
%
$H_\mathsf{D}{=}-\gamma/2$ provides a fair balance in training objectives, but
still suffers from inflexibility.
%
In contrast, being not susceptible to the mentioned problems of other choices,
HM[$\mathcal{S},g_\mathsf{LGA}$] achieves an ERS on par with
HM[$\mathcal{S},\mathcal{M}$], but is at the lowest R@1 performance penalty among all choices.
%
Its ERS is marginally lower than HM[$\mathcal{S},{-}\gamma/2$] because the
loss value eventually converges around ${-}\gamma/2$ due to optimization
difficulty, which means
adversarial triplets with $H_\mathsf{D}{\in}[{-}\gamma/2,0]$
are seldom used.

\begin{figure}[t]
	\vspace{-1.5em}
	\includegraphics[width=\columnwidth]{figics.pdf}
	\vspace{-1.9em}
	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'' in \cref{tab:ics}.}
\end{figure}

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it does
not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
{\bf{As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining higher robustness at a low training
cost, while retaining an acceptable trade-off in R@1.}}

>>>>

\begin{figure}[t]
	\vspace{-1.5em}
	\includegraphics[width=\columnwidth]{figgaeff.pdf}
	\vspace{-1.9em}
	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]'' in
	\cref{tab:gaeff}.}
	\vspace{-1em}
	\label{fig:gaeff}
\end{figure}

\noindent\textbf{II. Gradual Adversary.}
%
HM[$\mathcal{S},\mathcal{M}$] may still
suffer from the imbalance between learning the embeddings and gaining
adversarial robustness as discussed in \cref{sec:32}.
%
Hence, we conduct further experiments %with an improved $H_\mathsf{D}$
following the discussion, as shown in \cref{tab:gaeff} and \cref{fig:gaeff}.
%
Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness
with $g_\mathsf{B}(\cdot)$ benefits the ERS, but
results in a notably lower R@1;
%
A constant $H_\mathsf{D}$ at the upper bound of Semihard (\ie, $0$; too high
for both the early and the late phase of training) renders model collapse;
%
$H_\mathsf{D}$ at the lower bound (\ie, $-\gamma$; too low for the late phase)
leads to insignificant ERS improvement;
%
$H_\mathsf{D}{=}-\gamma/2$ provides a fair balance in training objectives, but
still suffers from inflexibility.
%
In contrast, being not susceptible to the mentioned problems of other choices,
HM[$\mathcal{S},g_\mathsf{LGA}$] achieves an ERS on par with
HM[$\mathcal{S},\mathcal{M}$], but is at the lowest R@1 performance penalty among all choices.
%
Its ERS is marginally lower than HM[$\mathcal{S},{-}\gamma/2$] because the
loss value eventually converges around ${-}\gamma/2$ due to optimization
difficulty, which means
adversarial triplets with $H_\mathsf{D}{\in}[{-}\gamma/2,0]$
are seldom created.

\begin{figure}[t]
	\vspace{-1.5em}
	\includegraphics[width=\columnwidth]{figics.pdf}
	\vspace{-1.9em}
	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'' in \cref{tab:ics}.}
	\vspace{-1em}
	\label{fig:icscurve}
\end{figure}

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it does
not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
{\bf{As shown in \cref{tab:ics} and \cref{fig:icscurve}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining higher robustness at a low training
cost, while retaining an acceptable trade-off in R@1.}}
